DATA 624 Homework 4

### 2020-02-29 DATA624/HW4.Rmd
More work on HW4

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(corrplot)
library(kableExtra)
```

@@

@@

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(corrplot)
library(Amelia)
library(kableExtra)
library(caret)
```

@@

**I am assuming the degenerate distibuted variaviables discussed earlier in the chapter referes to section 3.5 on removing predictors.  Here's some frequency tables:**

```{r, results='asis'}
for (predictor in names(select(Soybean, -Class))){
  temp <- Soybean %>%
    group_by(.dots=predictor) %>%
    tally() %>%
    arrange(desc(n)) 
  temp %>%
    summarise(total = sum(n)) %>%
    merge(temp) %>%
    mutate(share = n / total) %>%
    select(-total) %>%
    kable() %>%
    kable_styling() %>%
    print()
}
```

**There's a lot of missing variables. The authors recommended removing variables with near zero variance.  I know that the `caret` package has a function for that.  Here's the output from that function:**

```{r}
nearZeroVar(Soybean, saveMetrics = T) %>%
  kable() %>%
  kable_styling()
```

**There are three variables (`r names(Soybean)[caret::nearZeroVar(Soybean)]`) that have a near zero variance, and should probably be removed.**

@@

```{r}
Soybean %>%
  arrange(Class) %>%
  missmap(main = "Missing vs Observed")
```

**There are blocks of observations that are missing.  Since the data are arranged by the classes this suggests that the patterns of missing data are related to the classes.**

@@

**In my training it has been encouraged to never get rid of data, so my bias would be towards filling them with imputation.**

**I would first drop all missing variables and run it through a random forest to determine which variables are important.  If the near zero variance variables are not high in the list, I would drop them since they have little informational value.**

**If one of the important variables has a lot of missing data I would use k-means to fill in the holes with this categorical data.  If the variables were quantitative I would probably use the mean or median to fill in the holes.**
